Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-02-16 grove-paper.tex
drop old TODO comment block
replace \# with \multiVertex and \cycleVertex

A grove is a 4-tuple of the following form:
\[
  (e_r, MP, NP, W)
\]
where
\begin{align*}
  e_r &= \expr(v_0) \\
  MP &= \{\expr(v) : |\parents(v)| > 1\} \\
  NP &= \{\expr(v) : |\parents(v)| = 0 \land v \ne v_0\} \\
  W  &= \{\expr(v) : |\parents(v)| = 1 \wedge v = \min(\ancestors(v))\}
\end{align*}
For example, the grove corresponding to the graph in \autoref{fig:Decomposition example} is
\begin{align*}
  e_r &= \hole~\texttt{*}^{46}~\#48~\texttt{+}^{44}~\#48 \\
  MP &= \{x^{48}\} \\
  NP &= \{z^{58}\} \\
  W &= \{\hole~\texttt{+}^{52}~\#52~\texttt{*}^{54}~y^{56}\} \\
\end{align*}

@@

The second component $MP$ is the set of expressions derived from a vertex with multiple parents.
Wherever an edge to such a vertex appears, we place a reference to it $\#u$.
In the example, $x^{48}$ is referenced twice in $e_r$.

@@

% TODO: replace # with \multiVertex and \cycleVertex
% TODO: distinguish between multi-parent and cycle refs in text
% TODO: update \multiChild with more than 2 children and use it for conflict holes
% TODO: gray out ids in the grammar and expressions
% TODO: add a child to z^58 and rotate 51-52
% TODO: move example grove to right of its diagram
% TODO: use mathord for spaces around + / *
% TODO: figure out why + --> "" and * --> "\times"
% TODO: keep condensed "|"s for conflict holes in grammar, but not other places
% TODO: make lfp a math function

@@

We determine $e$ by starting at the root of the graph and including every connected
vertex that has a single parent. In positions where there are no children, we
leave an empty hole $\hole$. In positions where there are multiple children, we
leave a conflict hole of the form $\conflictHole{e_1,\ldots,e_n}$. Whenever we
encounter a vertex with multiple parents, we add its corresponding expression to
the second component $MP$ and leave an indirect reference $\#u$, where $u$ is
the unique identifier of the referenced vertex

>>>>

A grove is a 4-tuple of the following form:
\[
  (e_r, MP, NP, W)
\]
where
\begin{align*}
  e_r &= \expr(v_0) \\
  MP &= \{\expr(v) : |\parents(v)| > 1\} \\
  NP &= \{\expr(v) : |\parents(v)| = 0 \land v \ne v_0\} \\
  W  &= \{\expr(v) : |\parents(v)| = 1 \wedge v = \min(\ancestors(v))\}
\end{align*}
For example, the grove corresponding to the graph in \autoref{fig:Decomposition example} is
\begin{align*}
  e_r &= \hole~\texttt{*}^{40}~\multiVertex{42}~\texttt{+}^{38}~\multiVertex{42} \\
  MP &= \{x^{42}\} \\
  NP &= \{z^{52}\} \\
  W &= \{\hole~\texttt{+}^{46}~\cycleVertex{46}~\texttt{*}^{48}~y^{50}\} \\
\end{align*}

@@

The second component $MP$ is the set of expressions derived from a vertex with multiple parents.
Wherever an edge to such a vertex appears, we place a reference to it $\multiVertex{u}$.
In the example, $x^{48}$ is referenced twice in $e_r$.

@@

@@

We determine $e$ by starting at the root of the graph and including every connected
vertex that has a single parent. In positions where there are no children, we
leave an empty hole $\hole$. In positions where there are multiple children, we
leave a conflict hole of the form $\conflictHole{e_1,\ldots,e_n}$. Whenever we
encounter a vertex with multiple parents, we add its corresponding expression to
the second component $MP$ and leave an indirect reference $\multiVertex{u}$, where $u$ is
the unique identifier of the referenced vertex
